---
title: "MA710 - New York Times Articles"
author: "Yi Qi, Shu Zhang, Yirui Fan"
date: "3 Apr 2016"
output:
  html_document:
    toc: yes
---

\pagebreak


# Introduction

[Provide background for and an introduction to the dataset.
  Describe your intended analysis and goals.]
  
# Base investigation

[Start with a basic set of options, and explain why you chose them in the following table.]

[Do not change the first two lines of the table. They define the columns and the headers.]

Parameter | Value | Reason
--------- | ----- | ------
Query term | "dance" | Interested in modern dance.
Begin date | 1 Jan 2015 | Interested in 2015 articles.
End date   | 31 Dec 2015 | Interested in 2015 articles.
Field      | `snippet` | 
Stemming   | Yes/No | 
N-grams    | 1, 2 |
Stopwords  | "english"/"SMART" |
Stopwords  | "dance" | This is the search term.
Weighting  | binary | 
Threshold  | 2 |
Algorithm  | k-means | 
`k`        | 10 |

[Evaluate the clusters you create.]

### Evaluation: cluster counts 

The table below indicates the number of articles 
that are contained in each cluster. 
```{r echo=FALSE}
as.data.frame(table(cluster))
#  17  45   2   9   2  60 839  27   5   4 
```
[Interpret the information from the table. 
 Indicate which clusters are large enough to investigate further.
 Explain your reasoning.]

### Evaluation: common words 

[Use the `TopWords` function to check for common words in 
 each cluster which in the previous section you chose to 
 investigate further. 
 For each cluster indicate which words (if any) occur often enough
 to indicate a potential subject of the documents in the cluster.
 Indicate which clusters seem to have a potential subject and 
 should be investigated further.]


```{r echo=FALSE, warning=FALSE}
# The `TopWords` function displays the documents 
# in the cluster whose number is specified with 
# third parameter
TopWords(dtm, cluster, 1) 
```

[Explain whether the documents of this cluster have a common 
 subject and describe this subject. ]

```{r echo=FALSE, warning=FALSE}
# The `TopWords` function displays the documents 
# in the cluster whose number is specified with 
# third parameter
TopWords(dtm, cluster, 4) 
```

[Explain whether the documents of this cluster have a common 
 subject and describe this subject. ]

```{r echo=FALSE, warning=FALSE}
# The `TopWords` function displays the documents 
# in the cluster whose number is specified with 
# third parameter
TopWords(dtm, cluster, 10) 
```

[Explain whether the documents of this cluster have a common 
 subject and describe this subject. ]

### Evaluation: check documents  

[Use the `view.cluster` function to read the documents in each cluster 
 which you decided in the previous section should be investigated further.
 Look for a single subject common to all or most documents in the cluster.
 For each cluster indicate whether all or most of the documents in the 
 cluster share a common subject.]
 
```{r echo=FALSE}
view.cluster(1)
```

```{r echo=FALSE}
view.cluster(4)
```

```{r echo=FALSE}
view.cluster(10)
```


[From your evaluation, decide which parameter you will change for the next investigation.]

# Investigation 2

[Describe the option you will change from your previous investigation and why you choose it.
 Modify the following table to indicate the parameter choices you made for this investigation.
 Include the reasons you made these choices. If you did not change a parameter then simply
 copy the line from the previous table.]

Parameter | Value | Reason
--------- | ----- | ------
Query term | "dance" | Interested in modern dance.
Begin date | 1 Jan 2015 | Interested in 2015 articles.
End date   | 31 Dec 2015 | Interested in 2015 articles.
Field      | `snippet` | 
Stemming   | Yes/No | 
N-grams    | 1, 2 |
Stopwords  | "english"/"SMART" |
Stopwords  | "dance" | This is the search term.
Weighting  | binary | 
Threshold  | 2 |
`k`        | 10 |

[Evaluate the clusters you create.]

[From your evaluation, decide which parameter you will change for the next investigation.]

# Investigation ?

[Repeat this process until you are satisfied that you have found good clusters.]
  
# Conclusion

[Describe the final modifications used to create your clusters 
 and describe the clusters of the cluster group.]

[Explain why this is the best set of options/parameters and clusters.]
